Photo-D with LSST: stellar photometric distances out to the edge of the Galaxy

### 2024-08-28 paper/paper.tex
Minor edits.

\author[0000-0012-3245-123X]{Karlo Mrakov\v{c}i\'{c}}
\affiliation{Faculty of Physics, University of Rijeka, Radmile Matej\v{c}i\'{c} 2, 51000 Rijeka, Croatia}

@@

\author[0000-0000-0000-0000]{Connor Yablonski}
\affiliation{Department of Astronomy, University of Washington, Box 351580, Seattle, WA 98195, USA}

@@

\author[0000-0000-0000-0000]{Neven Caplar}
\affiliation{Department of Astronomy and DiRAC Institute, University of Washington, Box 351580, Seattle, WA 98195, USA}

\author[0000-0000-0000-0000]{Mario Juri\'{c}}
\affiliation{Department of Astronomy and DiRAC Institute, University of Washington, Box 351580, Seattle, WA 98195, USA}

@@

dust extinction plot in: 
BayesMethod3D_SEGUElong.ipynb

BDBS:
BDBS/analyzeBDBS_field_044_TRILEGALcatalog.ipynb
PhotoD/notebooks/BayesMethod3D_BDBSfield044.ipynb

IBJ2012: fig. 23 
star with g-i = 3.0 and r =20: DM = 7 mag so d=250 pc
Mr = 13

10% distance from both Gaia and LSST: fig. 21: 
sigmaPi = 0.5 mas for both LSST and Gaia
SNR=10, so pi = 5 mas or D=200 pc OK

within 150 pc: 10% dist for DM=6 and r = 21.5 => Mr = 15.5  (g-i = 3.6) 
LSST sigmaPi at r=21.5: 0.7 mas so pi = 7 mas or D = 150 pc!

blue star with g-i = 0.3 and r = 20: DM = 16, d=15 kpc
so Mr = 4
parallax = 1/15 mas so SNR=0.13

DM = 12: r = 16, d=2.5 kpc, pi = 0.4 
Gaia sigmaPi = 0.05 mas, SNR = 10 
LSST pi limited by systematics: sigmaPi = 0.5 so SNR~1

LSST at r = 24: sigmaPi = 3
for SNR=10, pi = 30 mas and d=30pc DM=2.5 mag
Mr = 24-2.5 -> Mr = 21.5

For stars with g-i > 3.2 (M5 and later), LSST has better parallax distance
estimates for r>20

For stars of any color at distances beyond 3 kpc, LSST photo distances
are better than Gaia distances
For blue stars at 3 kpc, r = 16 and Gaia's parallax are already 10\%
between 16 and 20, LSST benefits from FeH which photogeo don't have
LSST at blue end goes to 100 kpc with 10% distance, correct?

>>>>

\author[0009-0009-8154-3827]{Karlo Mrakov\v{c}i\'{c}}
\affiliation{Faculty of Physics, University of Rijeka, Radmile Matej\v{c}i\'{c} 2, 51000 Rijeka, Croatia}

@@

\author[0009-0000-0990-8339]{Connor Yablonski}
\affiliation{Department of Astronomy, University of Washington, Box 351580, Seattle, WA 98195, USA}

@@

\author[ 	
0000-0003-3287-5250]{Neven Caplar}
\affiliation{Department of Astronomy and DiRAC Institute, University of Washington, Box 351580, Seattle, WA 98195, USA}

\author[0000-0003-1996-9252]{Mario Juri\'{c}}
\affiliation{Department of Astronomy and DiRAC Institute, University of Washington, Box 351580, Seattle, WA 98195, USA}

@@
